---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Calibration and Validation

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
source("../functions.R")
config <- load_config("../../")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, comment = NA)

theme_set(theme_bw())
theme_update(
  strip.background = element_blank(),
  strip.text = element_text(face = "bold")
)

m_inp <- readRDS(file.path(config$wd, "model-input.rds"))
m_out <- readRDS(file.path(config$wd, "model-output.rds"))
m_diag <- readRDS(file.path(config$wd, "model-diagnostics.rds"))
calib <- m_diag$calib
valid <- m_diag$valid
```

After processing all of the data, the model was fitted using jags. The observation dataset was split into 80% for calibration, 20% for validation.

## Parameter Estimates

### Fixed Effects

```{r}
levels_fixed <- c(
  "intercept",
  "AreaSqKM",
  "impoundArea",
  "agriculture",
  "devel_hi",
  "forest",
  "prcp2",
  "prcp30",
  "prcp2.da",
  "prcp30.da",
  "airTemp.da",
  "airTemp.impoundArea",
  "airTemp.agriculture",
  "airTemp.forest",
  "airTemp.devel_hi",
  "airTemp.prcp2",
  "airTemp.prcp30",
  "airTemp.prcp2.da",
  "airTemp.prcp30.da"
)
param_fixed <- data_frame(
  var = factor(m_out$covs$fixed.ef, levels = levels_fixed, ordered = TRUE),
  mean = m_out$results$mean$B.0,
  q_025 = m_out$results$q2.5$B.0,
  q_975 = m_out$results$q97.5$B.0
) %>% 
  arrange(var)
```

Figure \@ref(fig:plot-params-fixed) and Table \@ref(tab:table-params-fixed) present the estimated mean and 95% credible region interval (CRI) of each fixed effect parameter. The intercept term is not shown in the figure because the values are much larger than the other parameters, and would thus skew the scale.

```{r plot-params-fixed, fig.height=6, fig.cap="Estimated Mean and 95% CRI of Fixed Effects"}
param_fixed %>% 
  filter(var != "intercept") %>% 
  mutate(
    var = ordered(var, levels = rev(levels(var)))
  ) %>% 
  ggplot(aes(var, mean)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_segment(aes(x = var, xend = var, y = q_025, yend = q_975), color = "deepskyblue") +
  geom_point(size = 2) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  coord_flip() +
  labs(
    x = "Fixed Effect Variable",
    y = "Estimated Mean and 95% CRI"
  )
```

```{r table-params-fixed}
param_fixed %>% 
  select(Variable = var, Mean = mean, `Lower CRI` = q_025, `Upper CRI` = q_975) %>% 
  knitr::kable(digits = 3, caption = "Estimated Mean and 95% CRI of Fixed Effects")
```

### HUC8 Random Effects 

```{r}
levels_huc8 <- c(
  "intercept.huc",
  "airTemp",
  "temp7p"
)

params_huc8 <- bind_rows(
  setNames(as_data_frame(m_out$results$mean$B.huc), m_out$covs$huc.ef) %>% 
    mutate(stat = "mean") %>% 
    bind_cols(m_out$ids$huc),
  setNames(as_data_frame(m_out$results$q2.5$B.huc), m_out$covs$huc.ef) %>% 
    mutate(stat = "q_025") %>% 
    bind_cols(m_out$ids$huc),
  setNames(as_data_frame(m_out$results$q97.5$B.huc), m_out$covs$huc.ef) %>% 
    mutate(stat = "q_975") %>% 
    bind_cols(m_out$ids$huc)
) %>% 
  gather(var, value, -stat, -huc8, -huc8_id) %>% 
  mutate(
    huc8 = factor(huc8, levels = rev(sort(unique(huc8))), ordered = TRUE),
    var = factor(var, levels = levels_huc8, ordered = TRUE)
  ) %>%  
  spread(stat, value) %>% 
  arrange(var, huc8_id)
```

Figure \@ref(fig:plot-params-huc8) shows the estimated mean and 95% credible region interval (CRI) for each random effect and HUC8. Table \@ref(tab:table-params-huc8) lists the estimated mean and 95% CRI of each parameter averaged over all HUC8s (mean value with standard deviation in parentheses).

```{r plot-params-huc8, fig.width=8, fig.height=10, fig.cap="Estimated Mean and 95% CRI of HUC Random Effects for Each HUC8"}
params_huc8 %>% 
  ggplot(aes(huc8, mean)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_segment(aes(x = huc8, xend = huc8, y = q_025, yend = q_975), color = "deepskyblue") +
  geom_point() +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 6)) +
  coord_flip() +
  facet_wrap(~ var, nrow = 1, scales = "free_x") +
  labs(
    x = "HUC8",
    y = "Estimated Mean and 95% CRI"
  ) +
  theme(
    axis.text.y = element_text(size = 6)
  )
```

```{r table-params-huc8}
params_huc8 %>% 
  gather(stat, value, mean, q_025, q_975) %>% 
  group_by(var, stat) %>% 
  summarise(
    n = n(),
    mean = mean(value),
    sd = sd(value)
  ) %>% 
  ungroup() %>% 
  mutate(
    label = paste0(sprintf("%.3f", mean), " (", sprintf("%.3f", sd), ")")
  ) %>% 
  select(var, stat, n, label) %>% 
  spread(stat, label) %>% 
  select(Variable = var, Count = n, Mean = mean, `Lower CRI` = q_025, `Upper CRI` = q_975) %>% 
  knitr::kable(align = "lrrrr", captio = "Mean and 95% CRI of HUC8 Random Effects Averaged Over All HUC8s (Mean Value and Std. Dev. in Parentheses)")
```

### Catchment Random Effects 

```{r}
levels_site <- c(
  "intercept.site",
  "airTemp",
  "temp7p"
)

params_site <- bind_rows(
  setNames(as_data_frame(m_out$results$mean$B.site), m_out$covs$site.ef) %>% 
    mutate(stat = "mean") %>% 
    bind_cols(m_out$ids$site),
  setNames(as_data_frame(m_out$results$q2.5$B.site), m_out$covs$site.ef) %>% 
    mutate(stat = "q_025") %>% 
    bind_cols(m_out$ids$site),
  setNames(as_data_frame(m_out$results$q97.5$B.site), m_out$covs$site.ef) %>% 
    mutate(stat = "q_975") %>% 
    bind_cols(m_out$ids$site)
) %>% 
  gather(var, value, -stat, -featureid, -featureid_id) %>% 
  mutate(
    featureid = factor(featureid, levels = rev(sort(unique(featureid))), ordered = TRUE),
    var = factor(var, levels = levels_site, ordered = TRUE)
  ) %>%  
  spread(stat, value) %>% 
  arrange(var, featureid_id)
```

Figure \@ref(fig:plot-params-catchment) shows the distribution of the estimated mean for each random effect term over all catchments. CRIs are not shown due to the large number of individual catchments (`r nrow(params_site)`). Table \@ref(tab:table-params-catchment) lists the estimated mean and 95% CRI of each parameter averaged over all catchments (mean value with standard deviation in parentheses).

```{r plot-params-catchment, fig.width=8, fig.height=3, fig.cap="Distribution of estimated mean for each random effect over all catchments"}
params_site %>% 
  ggplot(aes(mean)) +
  geom_histogram(bins = 30) +
  geom_vline(xintercept = 0, color = "black") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
  facet_wrap(~ var, nrow = 1, scales = "free") +
  labs(
    x = "Estimated Mean",
    y = "# Catchments"
  )
```

```{r table-params-catchment}
params_site %>% 
  gather(stat, value, mean, q_025, q_975) %>% 
  group_by(var, stat) %>% 
  summarise(
    n = n(),
    mean = mean(value),
    sd = sd(value)
  ) %>% 
  ungroup() %>% 
  mutate(
    label = paste0(sprintf("%.3f", mean), " (", sprintf("%.3f", sd), ")")
  ) %>% 
  select(var, stat, n, label) %>% 
  spread(stat, label) %>% 
  mutate(n = scales::comma(n)) %>% 
  select(Variable = var, Count = n, Mean = mean, `Lower CRI` = q_025, `Upper CRI` = q_975) %>% 
  knitr::kable(align = 'lrrrr', caption = "Estimated mean and 95% CRI for each random effect averaged over all catchments (mean value with std. dev. in parentheses)")
```

### Year Random Effects

```{r}
levels_year <- c(
  "intercept.year"
)

params_year <- bind_rows(
  setNames(as_data_frame(m_out$results$mean$B.year), m_out$covs$year.ef) %>% 
    mutate(stat = "mean") %>% 
    bind_cols(m_out$ids$year),
  setNames(as_data_frame(m_out$results$q2.5$B.year), m_out$covs$year.ef) %>% 
    mutate(stat = "q_025") %>% 
    bind_cols(m_out$ids$year),
  setNames(as_data_frame(m_out$results$q97.5$B.year), m_out$covs$year.ef) %>% 
    mutate(stat = "q_975") %>% 
    bind_cols(m_out$ids$year)
) %>% 
  gather(var, value, -stat, -year, -year_id) %>% 
  mutate(
    year = factor(year, levels = rev(sort(unique(year))), ordered = TRUE)
  ) %>%  
  spread(stat, value) %>% 
  arrange(var, year_id)
```

Figure \@ref(fig:plot-params-year) and Table \@ref(tab:table-params-year) present the mean and 95% CRI of the intercept term for each year. Recall that there are no random effects for years other than the intercept. 

```{r plot-params-year, fig.cap="Estimated Mean and 95% CRI of Intercept Random Effect for Each Year"}
params_year %>% 
  ggplot(aes(year, mean)) +
  geom_hline(yintercept = 0, color = "black") +
  geom_segment(aes(x = year, xend = year, y = q_025, yend = q_975), color = "deepskyblue") +
  geom_point(size = 2) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 10)) +
  coord_flip() +
  facet_wrap(~ var, nrow = 1, scales = "free_x") +
  labs(
    x = "Year",
    y = "Estimated Mean and 95% CRI"
  ) +
  theme(
    axis.text.y = element_text(size = 8)
  )
```

```{r table-params-year}
params_year %>% 
  select(Year = year, Mean = mean, `Lower CRI` = q_025, `Upper CRI` = q_975) %>% 
  knitr::kable(align = 'lrrrr', digits = 3, caption = "Estimated Mean and 95% CRI of Intercept Random Effect for Each Year")
```

## Goodness-of-Fit

### All Observations 

Table \@ref(tab:table-gof) summarizes the model goodness-of-fit for all observations in the calibration and validation datasets.

```{r table-gof}
stat_labels <- c(
  "n_obs" = "# Daily Observations",
  "n_deploy" = "# Time Series",
  "n_catchment" = "# Catchments",
  "n_huc8" = "# HUC8s",
  "n_year" = "# Years",
  "rmse" = "RMSE (degC)",
  "mean_resid" = "Mean Residual (degC)",
  "median_resid" = "Median Residual (degC)",
  "mean_abs_resid" = "Mean Absolute Residual (degC)",
  "median_abs_resid" = "Median Absolute Residual (degC)",
  "min_resid" = "Minimum Residual (degC)",
  "q01_resid" = "1st Percentile Residual (degC)",
  "q99_resid" = "99th Percentile Residual (degC)",
  "max_resid" = "Maximum Residual (degC)"
)
bind_cols(
  data_frame(
    dataset = c("calibration", "validation")
  ),
  as_data_frame(
    bind_rows(calib$summary, valid$summary)
  )
) %>%
  mutate_at(vars(starts_with("n_")), scales::comma) %>% 
  mutate_at(
    vars(
      rmse,
      mean_resid,
      median_resid,
      mean_abs_resid,
      median_abs_resid,
      min_resid,
      q01_resid,
      q99_resid,
      max_resid
    ),
    ~ sprintf("%.3f", .)
  ) %>% 
  select(dataset, starts_with("n_"), rmse, mean_resid, median_resid, mean_abs_resid, median_abs_resid, min_resid, q01_resid, q99_resid, max_resid) %>% 
  gather(stat, value, -dataset) %>% 
  spread(dataset, value) %>% 
  mutate(
    stat = factor(stat, ordered = TRUE, levels = names(stat_labels))
  ) %>% 
  arrange(stat) %>% 
  mutate(
    stat_label = plyr::revalue(stat, stat_labels)
  ) %>% 
  select(-stat) %>% 
  select(stat_label, calibration, validation) %>% 
  knitr::kable(
    align = "lrr", 
    col.names = c("", "Calibration", "Validation"),
    caption = "Summary statistics of model calibration and validation"
  )
```

Figure \@ref(fig:splot-calib-valid-pred) presents scatterplots of predicted vs. observed daily mean temperature for the calibration and validation datasets. The black line is the 1:1 line of equality. The red line is a linear regression trend line.

```{r splot-calib-valid-pred, fig.width=8, fig.height=4, fig.cap="Predicted versus Observed Daily Mean Temperature (degC) for Calibration and Validation Datasets"}
bind_rows(
  calib$values %>% 
    select(obs, pred) %>% 
    mutate(dataset = "Calibration"),
  valid$values %>% 
    select(obs, pred) %>% 
    mutate(dataset = "Validation")
) %>% 
  sample_frac(size = 0.1) %>% 
  ggplot(aes(obs, pred)) +
  geom_abline() +
  geom_point(size = 0.5, alpha = 0.25) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  coord_equal() +
  facet_wrap(~ dataset, nrow = 1) +
  labs(
    x = "Observed Temperature (degC)",
    y = "Predicted Temperature (degC)"
  ) +
  theme(aspect.ratio = 1)
```

### Deployments

Table \@ref(tab:table-gof-series) summarises the mean, median, minimum and maximum RMSE for each deployment (i.e. continuous timeseries of observations at a single location) in the calibration and validation datasets.

```{r table-gof-series}
stat_labels_deploy <- c(
  "n" = "# Time Series",
  "mean_rmse" = "Mean RMSE (degC)",
  "median_rmse" = "Median RMSE (degC)",
  "min_rmse" = "Minimum RMSE (degC)",
  "max_rmse" = "Maximum RMSE (degC)"
)
df_deploy <- bind_cols(
  data_frame(
    dataset = c("calibration", "validation"),
    data = list(
      calib$deploy %>% 
        select(-dataset),
      valid$deploy %>% 
        select(-dataset)
    )
  )
) %>% 
  mutate(
    data_best = map(data, function (x) {
      x %>% 
        filter(n >= 30) %>% 
        arrange(rmse) %>% 
        head(12)
    }),
    data_worst = map(data, function (x) {
      x %>% 
        filter(n >= 30) %>% 
        arrange(desc(rmse)) %>% 
        head(12)
    })
  )
df_deploy %>%
  mutate(
    n = map_dbl(data, nrow),
    mean_rmse = map_dbl(data, ~ mean(.$rmse)),
    median_rmse = map_dbl(data, ~ median(.$rmse)),
    min_rmse = map_dbl(data, ~ min(.$rmse)),
    max_rmse = map_dbl(data, ~ max(.$rmse))
  ) %>% 
  mutate_at(
    vars(
      mean_rmse, median_rmse, min_rmse, max_rmse
    ),
    ~ sprintf("%.3f", .)
  ) %>% 
  select(dataset, n, mean_rmse, median_rmse, min_rmse, max_rmse) %>% 
  gather(stat, value, -dataset) %>% 
  spread(dataset, value) %>% 
  mutate(
    stat = factor(stat, ordered = TRUE, levels = names(stat_labels_deploy))
  ) %>% 
  arrange(stat) %>% 
  mutate(
    stat_label = plyr::revalue(stat, stat_labels_deploy)
  ) %>% 
  select(-stat) %>% 
  select(stat_label, calibration, validation) %>% 
  knitr::kable(
    align = "lrr", 
    col.names = c("", "Calibration", "Validation"),
    caption = "Summary statistics of model calibration and validation RMSE for each deployment"
  )
```

Figure \@ref(fig:plot-hist-series-rmse) shows the distribution of deployment RMSE.

```{r plot-hist-series-rmse, fig.width=8, fig.height=3, fig.cap="Distribution of deployment RMSE"}
df_deploy %>% 
  unnest(data) %>% 
  ggplot(aes(rmse)) +
  geom_histogram(bins = 30) +
  geom_vline(
    data = df_deploy %>%
      mutate(
        mean_rmse = map_dbl(data, ~ mean(.$rmse))
      ),
    aes(xintercept = mean_rmse, color = "Mean RMSE")
  ) +
  scale_color_manual("", values = "red") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10), limits = c(0, NA)) +
  labs(
    x = "RMSE (degC)",
    y = "# Deployments"
  ) +
  facet_wrap(~ dataset, nrow = 1, scales = "free_y", labeller = labeller(dataset = c(
    "calibration" = "Calibration",
    "validation" = "Validation"
  )))
```

#### Calibration Deployment Examples

Figures \@ref(fig:plot-series-calib-best) to \@ref(fig:plot-series-calib-worst) show example deployments from the calibration dataset with the highest and lowest RMSE.

```{r plot-series-calib-best, fig.width=8, fig.height=10, fig.cap="Deployments with lowest RMSE in calibration dataset and n >= 30"}
df_deploy %>% 
  filter(dataset == "calibration") %>% 
  select(-data) %>% 
  unnest(data_best) %>% 
  mutate(
    label = paste0("Catchment ID: ", featureid, "\nDeployment ID = ", deploy_id," \nRMSE = ", sprintf("%.3f", rmse), ", n = ", scales::comma(n)),
    label = factor(label, ordered = TRUE, levels = label)
  ) %>% 
  unnest(data) %>% 
  ggplot(aes(date, obs)) +
  geom_line(aes(color = "Observed")) +
  geom_point(aes(color = "Observed"), size = 1) +
  geom_line(aes(y = pred, color = "Predicted")) +
  geom_point(aes(y = pred, color = "Predicted"), size = 1) +
  scale_color_manual("", values = c("Observed" = "black", "Predicted" = "red")) +
  scale_x_date(labels = scales::date_format("%b %d '%y")) +
  facet_wrap(~ label, scales = "free", nrow = 4) +
  labs(
    x = "Date",
    y = "Daily Mean Temperature (degC)",
    title = "Calibration | Lowest RMSE Deployments"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```

```{r plot-series-calib-worst, fig.width=8, fig.height=10, fig.cap="Deployments with highest RMSE in calibration dataset and n >= 30"}
df_deploy %>% 
  select(-data) %>% 
  filter(dataset == "calibration") %>% 
  unnest(data_worst) %>% 
  mutate(
    label = paste0("Catchment ID: ", featureid, "\nDeployment ID = ", deploy_id," \nRMSE = ", sprintf("%.3f", rmse), ", n = ", scales::comma(n)),
    label = factor(label, ordered = TRUE, levels = label)
  ) %>% 
  unnest(data) %>% 
  ggplot(aes(date, obs)) +
  geom_line(aes(color = "Observed")) +
  geom_point(aes(color = "Observed"), size = 1) +
  geom_line(aes(y = pred, color = "Predicted")) +
  geom_point(aes(y = pred, color = "Predicted"), size = 1) +
  scale_color_manual("", values = c("Observed" = "black", "Predicted" = "red")) +
  scale_x_date(labels = scales::date_format("%b %d '%y")) +
  facet_wrap(~ label, scales = "free", nrow = 4) +
  labs(
    x = "Date",
    y = "Daily Mean Temperature (degC)",
    title = "Calibration | Highest RMSE Deployments"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```

#### Validation Deployment Examples

Figures \@ref(fig:plot-series-valid-best) to \@ref(fig:plot-series-valid-worst) show example deployments from the validation dataset with the highest and lowest RMSE.

```{r plot-series-valid-best, fig.width=8, fig.height=10, fig.cap="Deployments with lowest RMSE in validation dataset and n >= 30"}
df_deploy %>% 
  select(-data) %>% 
  filter(dataset == "validation") %>% 
  unnest(data_best) %>% 
  mutate(
    label = paste0("Catchment ID: ", featureid, "\nDeployment ID = ", deploy_id," \nRMSE = ", sprintf("%.3f", rmse), ", n = ", scales::comma(n)),
    label = factor(label, ordered = TRUE, levels = label)
  ) %>% 
  unnest(data) %>% 
  ggplot(aes(date, obs)) +
  geom_line(aes(color = "Observed")) +
  geom_point(aes(color = "Observed"), size = 1) +
  geom_line(aes(y = pred, color = "Predicted")) +
  geom_point(aes(y = pred, color = "Predicted"), size = 1) +
  scale_color_manual("", values = c("Observed" = "black", "Predicted" = "red")) +
  scale_x_date(labels = scales::date_format("%b %d '%y")) +
  facet_wrap(~ label, scales = "free", nrow = 4) +
  labs(
    x = "Date",
    y = "Daily Mean Temperature (degC)",
    title = "Validation | Lowest RMSE Deployments"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```

```{r plot-series-valid-worst, fig.width=8, fig.height=8, fig.cap="Deployments with highest RMSE in validation dataset and n >= 30"}
df_deploy %>% 
  select(-data) %>% 
  filter(dataset == "validation") %>% 
  unnest(data_worst) %>% 
  mutate(
    label = paste0("Catchment ID: ", featureid, "\nDeployment ID = ", deploy_id," \nRMSE = ", sprintf("%.3f", rmse), ", n = ", scales::comma(n)),
    label = factor(label, ordered = TRUE, levels = label)
  ) %>% 
  unnest(data) %>% 
  ggplot(aes(date, obs)) +
  geom_line(aes(color = "Observed")) +
  geom_point(aes(color = "Observed"), size = 1) +
  geom_line(aes(y = pred, color = "Predicted")) +
  geom_point(aes(y = pred, color = "Predicted"), size = 1) +
  scale_color_manual("", values = c("Observed" = "black", "Predicted" = "red")) +
  scale_x_date(labels = scales::date_format("%b %d '%y")) +
  facet_wrap(~ label, scales = "free", nrow = 4) +
  labs(
    x = "Date",
    y = "Daily Mean Temperature (degC)",
    title = "Validation | Highest RMSE Deployments"
  ) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```


### Catchments

Table \@ref(tab:table-gof-catchment) summarises the mean, median, minimum and maximum RMSE of all catchments in the calibration and validation datasets.

```{r table-gof-catchment}
stat_labels_catchment <- c(
  "n" = "# Time Series",
  "mean_rmse" = "Mean RMSE (degC)",
  "median_rmse" = "Median RMSE (degC)",
  "min_rmse" = "Minimum RMSE (degC)",
  "max_rmse" = "Maximum RMSE (degC)"
)
df_catchment <- bind_cols(
  data_frame(
    dataset = c("calibration", "validation"),
    data = list(
      calib$catchment %>% 
        select(-dataset),
      valid$catchment %>% 
        select(-dataset)
    )
  )
)
df_catchment %>%
  mutate(
    n = map_dbl(data, nrow),
    mean_rmse = map_dbl(data, ~ mean(.$rmse)),
    median_rmse = map_dbl(data, ~ median(.$rmse)),
    min_rmse = map_dbl(data, ~ min(.$rmse)),
    max_rmse = map_dbl(data, ~ max(.$rmse))
  ) %>% 
  mutate_at(
    vars(
      mean_rmse, median_rmse, min_rmse, max_rmse
    ),
    ~ sprintf("%.3f", .)
  ) %>% 
  select(dataset, n, mean_rmse, median_rmse, min_rmse, max_rmse) %>% 
  gather(stat, value, -dataset) %>% 
  spread(dataset, value) %>% 
  mutate(
    stat = factor(stat, ordered = TRUE, levels = names(stat_labels_catchment))
  ) %>% 
  arrange(stat) %>% 
  mutate(
    stat_label = plyr::revalue(stat, stat_labels_catchment)
  ) %>% 
  select(-stat) %>% 
  select(stat_label, calibration, validation) %>% 
  knitr::kable(
    align = "lrr", 
    col.names = c("", "Calibration", "Validation"),
    caption = "Summary of catchment RMSE values for calibration and validation datasets"
  )
```

Figure \@ref(fig:plot-hist-catchment-rmse) shows the distribution of catchment RMSE.

```{r plot-hist-catchment-rmse, fig.width=8, fig.height=3, fig.cap="Distribution of catchment RMSE"}
df_catchment %>% 
  unnest(data) %>% 
  ggplot(aes(rmse)) +
  geom_histogram(bins = 30) +
  geom_vline(
    data = df_deploy %>%
      mutate(
        mean_rmse = map_dbl(data, ~ mean(.$rmse))
      ),
    aes(xintercept = mean_rmse, color = "Mean RMSE")
  ) +
  scale_color_manual("", values = "red") +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10), limits = c(0, NA)) +
  labs(
    x = "RMSE (degC)",
    y = "# Catchments"
  ) +
  facet_wrap(~ dataset, nrow = 1, scales = "free_y", labeller = labeller(dataset = c(
    "calibration" = "Calibration",
    "validation" = "Validation"
  )))
```

